---
title: "Scenarios"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Scenarios}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
n_runs <- nrow(keys.lid::performances)
seconds_per_run <- 30
run_total <- n_runs * seconds_per_run / 3600
run_total_hours <- round(run_total,0)
run_total_minutes <- round(60*(run_total - run_total_hours),0) 

#keys.lid::performances
```

## Scenarios

```{r setup}
library(keys.lid)

paths_list <- list(
  swmm_exe = "C:/Program Files (x86)/EPA SWMM 5.1.015/swmm5.exe"
  )

paths <- kwb.utils::resolve(paths_list)


scenarios <- keys.lid::read_scenarios()

DT::datatable(scenarios)


```
## Simulate Performance

The SWMM simulations (years: 2008 - 2019) and calculation of 
performance metrics (volume rainfall retended, rainfall event sums/max) for four 
LIDs with different parameterisations and for five different climate zones 
in China (in total: `r n_runs` model runs, which takes about `r seconds_per_run` `seconds per run`, i.e. in total `r run_total_hours` hours  `r run_total_minutes` minutes on my laptop).

```{r simulate_performances, eval = FALSE}

### takes about 2.5h for all four LIDs to simulate
catchment_area_m2 <- 1000
lid_area_fractions <- c(0,0.5,1)

### Bioretention Cell
br <- keys.lid::simulate_performances(
  lid_selected = scenarios[scenarios$lid_name_tidy == "bioretention_cell",],
  lid_area_fractions = lid_area_fractions,
  catchment_area_m2 = catchment_area_m2,
  swmm_exe = paths$swmm_exe
)

### Green Roof
gr <- keys.lid::simulate_performances(
  lid_selected = scenarios[scenarios$lid_name_tidy == "green_roof",],
  lid_area_fractions = lid_area_fractions,
  catchment_area_m2 = catchment_area_m2,
  swmm_exe = paths$swmm_exe
)

### Permeable Pavement
pp <- keys.lid::simulate_performances(
  lid_selected = scenarios[scenarios$lid_name_tidy == "permeable_pavement",],
  lid_area_fractions = lid_area_fractions,
  catchment_area_m2 = catchment_area_m2,
  swmm_exe = paths$swmm_exe
)

### Rain Barrel
rb <- keys.lid::simulate_performances(
  lid_selected = scenarios[scenarios$lid_name_tidy == "rain_barrel",],
  lid_area_fractions = lid_area_fractions,
  catchment_area_m2 = catchment_area_m2,
  swmm_exe = paths$swmm_exe
)

performances <- br %>%
  dplyr::bind_rows(gr) %>%
  dplyr::bind_rows(pp) %>%
  dplyr::bind_rows(rb)

```

## Evaluate Performance

### Median Volume Rainfall Retended per Year

#### Bioretention Cell 

```{r evaluate_performance_vrr_br, fig.height=7, fig.width=7}

keys.lid::plot_vrr_median("bioretention_cell")

```

#### Green Roof 

```{r evaluate_performance_vrr_gr, fig.height=7, fig.width=7}

keys.lid::plot_vrr_median("green_roof")

```

#### Permeable Pavements 

```{r evaluate_performance_vrr_pp, fig.height=7, fig.width=7}

keys.lid::plot_vrr_median("permeable_pavement")

```

#### Rain Barrel

```{r evaluate_performance_vrr_rr, fig.height=7, fig.width=7}

keys.lid::plot_vrr_median("rain_barrel")

```

### Boxplots

Example for LID **green roof** in **climate zones 1 and 5**

#### Volume Rainfall Retended 

**Zone 1**

```{r evaluate_performance_boxplot_vrr_gr_zone1, fig.height=7, fig.width=7}

keys.lid::boxplot_vrr(lid = "green_roof", zone_id = 1)

```

**Zone 2**

```{r evaluate_performance_boxplot_vrr_gr_zone2, fig.height=7, fig.width=7}

keys.lid::boxplot_vrr(lid = "green_roof", zone_id = 2)

```

**Zone 3**

```{r evaluate_performance_boxplot_vrr_gr_zone3, fig.height=7, fig.width=7}

keys.lid::boxplot_vrr(lid = "green_roof", zone_id = 3)

```

**Zone 4**

```{r evaluate_performance_boxplot_vrr_gr_zone4, fig.height=7, fig.width=7}

keys.lid::boxplot_vrr(lid = "green_roof", zone_id = 4)

```

**Zone 5**

```{r evaluate_performance_boxplot_vrr_gr_zone5, fig.height=7, fig.width=7}

keys.lid::boxplot_vrr(lid = "green_roof", zone_id = 5)

```

#### Runoff Maximum per Event 

**Zone 1**

```{r evaluate_performance_boxplot_runoff_max_gr_zone1, fig.height=7, fig.width=7}

keys.lid::boxplot_runoff_max(lid = "green_roof", zone_id = 1)

```
**Zone 5**

```{r evaluate_performance_boxplot_runoff_max_gr_zone5, fig.height=7, fig.width=7}

keys.lid::boxplot_runoff_max(lid = "green_roof", zone_id = 5)

```

#### Runoff Volume per Event 

**Zone 1**

```{r evaluate_performance_boxplot_runoff_volume_gr_zone1, fig.height=7, fig.width=7}

keys.lid::boxplot_runoff_volume(lid = "green_roof", zone_id = 1)

```
**Zone 5**

```{r evaluate_performance_boxplot_runoff_volume_gr_zone5, fig.height=7, fig.width=7}

keys.lid::boxplot_runoff_volume(lid = "green_roof", zone_id = 5)

```
